DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-29 ase2017/paper.tex
ase
Signed-off-by: aabate <aabate@cs.ox.ac.uk>

Our CEGIS engine is implemented as an integrated module within the bounded model checker CBMC~\cite{cbmc}.  CBMC
transforms an ANSI-C representation of our closed-loop control system models into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and quantization noise explicitly using CBMC's
nondeterminism API.  Our module was included in CBMC~5.7 and is available for
download\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}.  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}.  The current development branch
of our tool is available in a public GitHub
repository\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.

@@

\begin{enumerate}
\item \textbf{Setup}: obtains the physical plant, fixed-point format 
and dynamic input ranges, and translates them to a specific structure in MATLAB;
\item \textbf{Parse}: obtains the digital system specification and translates 
it into an ANSI-C program;
\item \textbf{Execution}: obtains the ANSI-C program from the previous step 
and calls our CEGIS engine as back-end program synthesis tool to perform the automated synthesis;
\item \textbf{Extraction}: obtains the ``.log'' file that is generated 
after the synthesis phase and then checks the synthesized digital-controller;
\item \textbf{Report}: obtains the digital controller from the previous step 
and translates it into the MATLAB structures to show the respective result to the user.
\end{enumerate}

@@

\begin{itemize}
\item \textbf{Representation}: the synthesis can be 
performed for digital systems specified as 
transfer-function or state-space equations;
\item \textbf{Fixed-Point Arithmetic}: the digital 
controller is synthesized considering FWL effects, 
in fixed-point numeric representation;
\item \textbf{Interface}: the synthesis can be executed 
via command-line or graphical-user interface (GUI). 
For the GUI application, the user can plot the step response 
to reproduce the stability in closed-loop of the synthesized digital controller;
\end{itemize}

@@

Users must provide a digital system described as a MATLAB system 
using a \texttt{tf} (for transfer-function) or an \texttt{ss} (for state-space) 
command (cf. step $1$ of Fig.~\ref{fig:synthesis-flow}).
\tool is called via command line in MATLAB as

@@

\noindent where \texttt{plant} is the physical plant in state-space or transfer-function representation, 
\texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR} 
are the maximum and minimum dynamic range, respectively (cf. steps $2$ and $3$ of Fig.~\ref{fig:synthesis-flow}).
%
After executing the \texttt{synthesize} command in MATLAB, 
\tool provides the synthesized digital controller, according to 
the digital system representation, {\it i.e.}, transfer-function or 
state-space equations.

@@

A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; 
poles must have the modulus less than one. In order to compute the poles for the digital 
system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
to achieve a general equation regarding the transfer function representation. 
The general equation that represents the combination between Equations~\eqref{equation_plant}
and~\eqref{equation_controller} is
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
\end{equation}

@@

\tool can synthesize digital controllers for dynamic physical plants, 
represented in MATLAB through transfer-function and state-space,  
w.r.t. stability and safety, using the CEGIS approach. 
%
Given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its digital implementation (fixed-point arithmetic). 
%
As future work, \tool will perform synthesis of other types of specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties (e.g., presence of limit cycles).

>>>>

Our CEGIS engine is implemented as an integrated module within the bounded model checker CBMC~\cite{cbmc}.  CBMC
transforms an ANSI-C representation of our closed-loop control system model into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
nondeterminism API.  Our module was included in CBMC~5.7 and is available for
download\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}.  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}.  The current development branch
of our tool is available in a public GitHub
repository\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.

@@

\begin{enumerate}
\item \textbf{Setup}: obtains the physical plant, fixed-point format 
and dynamic input ranges, and translates them to a specific structure in MATLAB;
\item \textbf{Parse}: obtains the digital system specification and translates 
it into an ANSI-C program;
\item \textbf{Execution}: obtains the ANSI-C program from the previous step 
and calls our CEGIS engine as a back-end program synthesis tool to perform the automated synthesis;
\item \textbf{Extraction}: obtains the ``.log'' file that is generated 
after the synthesis phase and then checks the synthesized digital-controller;
\item \textbf{Report}: obtains the digital controller from the previous step 
and translates it into the MATLAB structures to show the respective result to the user.
\end{enumerate}

@@

\begin{itemize}
\item \textbf{Representation}: the synthesis can be 
performed for digital systems specified via 
transfer function or as state-space models;
\item \textbf{Fixed-Point Arithmetic}: the digital 
controller is synthesized considering FWL effects, 
in fixed-point numeric representation;
\item \textbf{Interface}: the synthesis can be executed 
via command-line or graphical-user interface (GUI). 
For the GUI application, the user can plot the step response 
to reproduce the stability in closed-loop of the synthesized digital controller;
\end{itemize}

@@

Users must provide a digital system described as a MATLAB model 
using a \texttt{tf} (for transfer function) or an \texttt{ss} (for state-space model) 
command (cf. step $1$ of Fig.~\ref{fig:synthesis-flow}).
\tool is called via command line in MATLAB as

@@

\noindent where \texttt{plant} is the physical plant in state-space or transfer function representation, 
\texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR} 
are the maximum and minimum dynamic range, respectively (cf. steps $2$ and $3$ of Fig.~\ref{fig:synthesis-flow}).
%
After executing the \texttt{synthesize} command in MATLAB, 
\tool provides the synthesized digital controller, according to the digital system representation.

@@

A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unity circle, 
namely poles must have the modulus less than one. In order to compute the poles for the digital 
system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
to achieve a general equation regarding the transfer function representation. 
The general equation that represents the combination between Equations~\eqref{equation_plant}
and~\eqref{equation_controller} is
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
\end{equation}

@@

\tool can synthesize digital controllers for dynamic physical plants, 
represented in MATLAB as a transfer function or a state-space model,  
w.r.t. stability and safety, using the CEGIS approach. 
%
Given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its digital implementation (fixed-point arithmetic). 
%
As future work, \tool will perform synthesis of other types of specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties (e.g., presence of limit cycles).
